Online Verification of Commutativity

### 2020-08-02 acmPaper/paper.tex
fix labeling/refs

\subsection{Comparison of algorithm time cost}
The average time taken by each algorithm over the course of 10 runs over randomly generated graphs with 9 nodes and 32 edges is listed in table ~\ref{times}.

\begin{figure}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Naive baseline & 0.77 \\
    Two Flip tolerant & 0.075 \\
    Batch algorithm & 7.55 \\
    ~\ref{algo_online_polynomial} & 0.0038 \\
    ~\ref{algo_online_minimal} & 0.00086 \\
    \hline
\end{tabular}
\label{times} %TODO debug and fix label not working.
\caption{Computation time for 9 node graph of density 0.4, averaged over ten runs}
\end{figure}

@@

Algorithms scale as expected with time, as seen in figure ~\ref{fig:timeVsSize}. 
Both algorithm ~\ref{algo_online_minimal} and ~\ref{algo_minimal_spanning_set} exhibit graphs that are polynomial in appearance, as does the batch baseline.
\xxx[AK]{Do I need to justify this by doing some kind of fit?}
The naive baseline as well as the two flip tolerant baseline display growth that quickly makes computation untenable.
The batch algorithm also grows quickly.

We define density to be the ratio of the number of edges in the graph to the total possible number of edges ($|V|^2$, where $|V|$ is the number of nodes).
Run time relates to the density of edges in the input graph.
The degree of the effect differs with the algorithms, as figure ~\ref{fig:timeVsSize} shows.
Generally, denser graphs entail longer computation time.
% Our proposed algorithms, ~\ref{algo_minimal_spanning_set} and ~\ref{algo_online_polynomial} are less affected because they aggressively remove redundancies.

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimal}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomial}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_NaiveChecker.png}
      \caption{Naive baseline}
      \label{fig:sfigNaive}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_TwoFlipPathChecker.png}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlip}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_BatchChecker.png}
      \caption{Batch algorithm baseline}
      \label{fig:sfigBatch}
    \end{subfigure}

    \label{fig:timeVsSize}
    \caption{Plots of scaling of time with input size and density}
\end{figure}

\subsection{Variance}
The periodic spikes in figure ~\ref{fig:sfigOptimal} are striking. 
We plot the spread of results to understand what is happening.
We find ~\ref{algo_online_minimal} has outliers about two standard deviation above the mean responsible for the spikes in the average.
The outliers themselves follow a polynomial curve.
The plots in figure ~\ref{fig:variance} depict the situation.
Grey points are the results of evaluation on individual points, and error bars show standard deviation. 
The black curve traces the mean.
No such effect is observed in ~\ref{algo_online_polynomial}.
\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{variance_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimal}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{variance_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomial}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{variance_10_TwoFlip.png}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlip}
    \end{subfigure}

    \label{fig:variance}
    \caption{Plots of spread of results}
\end{figure}

\subsection{Size of Output}
Output size is a metric of interest, should the equality checking oracle be expensive.
Table ~\ref{sizes}, summarizes the number of output pairs that the algorithms returned on average over 10 runs, for graphs with 9 nodes and 32 edges.
\begin{figure}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Naive baseline & 39754.9 \\
    Two Flip tolerant & 748.9 \\
    Batch algorithm & 23 \\
    algorithm ~\ref{algo_online_polynomial} & 78.3 \\
    algorithm ~\ref{algo_online_minimal} & 1 \\
    \hline
\end{tabular}
\label{sizes} % Now working. TODO fix label.
\caption{Output size for 9 node graph of density 0.4, averaged over ten runs}
\end{figure}

>>>>

\subsection{Comparison of algorithm time cost}
The average time taken by each algorithm over the course of 10 runs over randomly generated graphs with 9 nodes and 32 edges is listed in table ~\ref{tab:times}.

\begin{table}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average seconds of computation \\
    \hline
    Naive baseline & 0.77 \\
    Two Flip tolerant & 0.075 \\
    Batch algorithm & 7.55 \\
    ~\ref{algo_online_polynomial} & 0.0038 \\
    ~\ref{algo_online_minimal} & 0.00086 \\
    \hline
\end{tabular}
\caption{Computation time for 9 node graph of density 0.4, averaged over ten runs}
\label{tab:times} %TODO debug and fix label not working.
\end{table}

@@

Algorithms scale as expected with time, as seen in figure ~\ref{fig:timeVsSize}. 
Both ~\ref{algo_online_minimal} and ~\ref{algo_minimal_spanning_set} exhibit graphs that are polynomial in appearance, as does the batch baseline.
\xxx[AK]{Do I need to justify this by doing some kind of fit?}
The naive baseline as well as the two flip tolerant baseline display growth that quickly makes computation untenable.
The batch algorithm also grows fast, though not as much as the online checking baselines.

We define density to be the ratio of the number of edges in the graph to the total possible number of edges ($|V|^2$, where $|V|$ is the number of nodes).
Run time relates to the density of edges in the input graph.
The degree of the effect differs with the algorithms, as figure ~\ref{fig:timeVsSize} shows.
Generally, denser graphs entail longer computation time.
For the batch algorithm we use lower densities since the input graph must be acyclic. This puts an upper bound on density that approaches 0.5 in large graphs.
% Our proposed algorithms, ~\ref{algo_minimal_spanning_set} and ~\ref{algo_online_polynomial} are less affected because they aggressively remove redundancies.

\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalTvsS}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialTvsS}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_NaiveChecker.png}
      \caption{Naive baseline}
      \label{fig:sfigNaiveTvsS}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_TwoFlipPathChecker.png}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlipTvsS}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{timeVsSize_10_BatchChecker.png}
      \caption{Batch algorithm baseline}
      \label{fig:sfigBatchTvsS}
    \end{subfigure}
    \caption{Plots of scaling of time with input size and density}
    \label{fig:timeVsSize}
\end{figure}

\subsection{Variance}
The periodic spikes in figure ~\ref{fig:sfigOptimalTvsS} are striking. 
We plot the spread of results to understand what is happening.
We find ~\ref{algo_online_minimal} has outliers about two standard deviation above the mean responsible for the spikes in the average.
The outliers themselves follow a polynomial curve.
The plots in figure ~\ref{fig:variance} depict the situation.
Grey points are the results of evaluation on individual points, and error bars show standard deviation. 
The black curve traces the mean.
No such effect is observed in ~\ref{algo_online_polynomial}.
\begin{figure}
    % TODO format nicely.
    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{variance_10_OptimalSet.png}
      \caption{~\ref{algo_online_minimal}}
      \label{fig:sfigOptimalSpread}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{variance_10_Polynomial.png}
      \caption{~\ref{algo_online_polynomial}}
      \label{fig:sfigPolynomialSpread}
    \end{subfigure}

    \begin{subfigure}{.4\textwidth}
      \includegraphics[width=.8\linewidth]{variance_10_TwoFlip.png}
      \caption{Two flip tolerant baseline}
      \label{fig:sfigTwoFlipSpread}
    \end{subfigure}

    \caption{Plots of spread of results}
    \label{fig:variance}
\end{figure}

\subsection{Size of Output}
Output size is a metric of interest, should the equality checking oracle be expensive.
Table ~\ref{tab:sizes}, summarizes the number of output pairs that the algorithms returned on average over 10 runs, for graphs with 9 nodes and 32 edges.
\begin{table}
\begin{tabular}{|c|c|}
    \hline
    Algorithm & average number of output pairs \\
    \hline
    Naive baseline & 39754.9 \\
    Two Flip tolerant & 748.9 \\
    Batch algorithm & 23 \\
    ~\ref{algo_online_polynomial} & 78.3 \\
    ~\ref{algo_online_minimal} & 1 \\
    \hline
\end{tabular}
\caption{Output size for 9 node graph of density 0.4, averaged over ten runs}
\label{tab:sizes}
\end{table}
